---
title: "Regression Model"
output: html_document
date: "2023-12-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE) 
knitr::opts_chunk$set(warning = FALSE) 
options(kableExtra.auto_format = FALSE)
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
knitr::knit_engines$set(text = function(options) {
  code <- paste(options$code, collapse = "\n")
})
knitr::opts_chunk$set(message=FALSE, tidy.opts=list(width.cutoff=75), tidy=TRUE) 
```

```{r}
library(tidycensus)
library(tidyverse)
library(readr)
library(survey)
library(srvyr)
library(convey)
library(dplyr)
library(tidyr)
library(plm)
library(ineq)
library(ggplot2)
library(scales)
library(car)
library(gtsummary)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(stargazer)
library(knitr)
library(kableExtra)
```


```{r}
filtered <- read.csv('filtered.csv')
```

# Regression Models
```{r}
#as survey
filtersurvey <- svydesign(id=~1, weights=~WTSURVY, data=filtered)
```

## Earnings and fields of study

$$
ln(Annual Salary) = \beta_0 + \beta_{i} FOS_i + \gamma_j X_j + \epsilon_{ij}
$$

$$
FOD_i = \{CompSci, Biology, Physical, Engineering, Health, Management, Education, Arts, Other\}
$$

$$
X_j = \{Age,Gender, Race, Graduation Year, Parents Education Level...\}
$$

```{r}
lnmajor <- svyglm(log(Salary)~CompSci + Biology + Physical+Engineering+Health+Management+Education
            +Arts+Other
            , filtersurvey)
summary(lnmajor)
#100*(exp(coefficients(lnmajorage))-1)
```

```{r}
lnmajorage <- svyglm(log(Salary)~CompSci + Biology + Physical+Engineering+Health+Management+Education
            +Arts+Other+Age
            , filtersurvey)
summary(lnmajorage)
```

```{r}
lnmajorcontrol <- svyglm(log(Salary)~CompSci + Biology+Physical+Engineering+Health+
                     Management+Education+Arts+Other + Age + Minority + Disable 
                   + Citizen, filtersurvey)
summary(lnmajorcontrol)
```


correction to get the percentage change in the salary
100*(exp(beta)-1)


## Earnings within each gender 
Model on gender

```{r}
filteredF <- filtered %>%
  filter(Female == 1)

filteredM <- filtered %>%
  filter(Female == 0)

filteredF <- svydesign(id=~1, weights=~WTSURVY, data=filteredF)
filteredM <- svydesign(id=~1, weights=~WTSURVY, data=filteredM)
```

```{r}
F1 <- svyglm(log(Salary)~CompSci + Biology+Physical+Engineering+Health+
                     Management+Education+Arts+Other 
            , filteredF)
summary(F1)
```

```{r}
F2 <- svyglm(log(Salary)~CompSci + Biology+Physical+Engineering+Health+
                     Management+Education+Arts+Other + Age + Minority + Disable + Citizen, filteredF)
summary(F2)
```

```{r}
F3 <- svyglm(log(Salary)~CompSci + Biology+Physical+Engineering+Health+
                     Management+Education+Arts+Other + Age + Minority + Disable + Citizen + HSDAD + HSMOM + Private, filteredF)
summary(F3)
```

```{r}
M1 <- svyglm(log(Salary)~CompSci + Biology+Physical+Engineering+Health+
                     Management+Education+Arts+Other 
            , filteredM)
summary(M1)
```

```{r}
M2 <- svyglm(log(Salary)~CompSci + Biology+Physical+Engineering+Health+
                     Management+Education+Arts+Other + Age + Minority + Disable + Citizen, filteredM)
summary(M2)
```

```{r}
M3 <- svyglm(log(Salary)~CompSci + Biology+Physical+Engineering+Health+
                     Management+Education+Arts+Other + Age + Minority + Disable + Citizen + HSDAD + HSMOM + Private, filteredM)
summary(M3)
```

## Interaction of fields of study and gender
Within major difference for female and male
$$
ln(Annual Salary) = \beta_0 + \beta_{1i} Female:FOS_i + \beta_{2i}FOS_i + \gamma_j X_j + \epsilon_{ij}
$$

```{r}
gender <- svyglm(log(Salary) ~ CompSci:Female + Arts:Female + Biology:Female + 
    Engineering:Female + Physical:Female + Health:Female + Management:Female + 
    Education:Female + Other:Female + SocialSci:Female + 
    CompSci + Biology + Physical + Engineering + Health + Management + 
    Education + Arts + Other , design=filtersurvey)
summary(gender)

#summary <- sjt.lm(gender, reorder.terms = ~ reorder(carb))
```

```{r}
gendercontrol <- svyglm(log(Salary) ~ CompSci:Female + Arts:Female + Biology:Female + 
    Engineering:Female + Physical:Female + Health:Female + Management:Female + 
    Education:Female + Other:Female + SocialSci:Female + 
    CompSci + Biology + Physical + Engineering + Health + Management + 
    Education + Arts + Other + Age + Minority + Disable + Citizen, design=filtersurvey)
summary(gendercontrol)

```

```{r}
gendercontrol2 <- svyglm(log(Salary) ~ CompSci:Female + Arts:Female + Biology:Female + 
    Engineering:Female + Physical:Female + Health:Female + Management:Female + 
    Education:Female + Other:Female + SocialSci:Female + 
    CompSci + Biology + Physical + Engineering + Health + Management + 
    Education + Arts + Other + Age + Minority + Disable + Citizen +
    HSDAD + HSMOM + Private, design=filtersurvey)
summary(gendercontrol2)
```


# Visualize the results

Model 1: ln(Annual Salary) = \beta_0 + \beta_{i} FOS_i + \epsilon_{ij}

```{r}
majcof <- lnmajor$coefficients[2:10] 
baseline <- 0


majcof <- data.frame(Category = names(majcof), Value = majcof)


t_shift <- scales::trans_new("shift",
                             transform = function(x) {x-baseline},
                             inverse = function(x) {x+baseline})
majcof$Category <- factor(majcof$Category, levels=majcof$Category[order(majcof$Value)])


ggplot(majcof, aes(x = reorder(Category,Value), y = (Value+baseline), fill = Category, colour = Category)) + 
  geom_bar(stat="identity") +
  scale_y_continuous(trans = t_shift, label=comma)+
  geom_hline(yintercept = baseline, linetype = "dashed", color = "red") +
  labs(title = "Earnings Inequality without control: 'Social Science' as baseline", x = "Fields of Study", y = "Earnings Differential") +
  geom_text(aes(label = signif(Value)), nudge_y = 0.05, vjust = 0.5, color="black", size=3)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


Model 2: ln(Annual Salary) = \beta_0 + \beta_{i} FOS_i + \gamma_j X_j + \epsilon_{ij}

```{r}
majctrl <- lnmajorcontrol$coefficients[2:10]

baselinectrl <- 0

majctrl <- data.frame(Category = names(majctrl), Value = majctrl)

majctrl$Category <- factor(majctrl$Category, levels=majctrl$Category[order(majctrl$Value)])

ggplot(majctrl, aes(x = reorder(Category,Value), y = Value, fill = Category, colour = Category)) + 
  geom_bar(stat="identity") +
  scale_y_continuous(label=comma)+
  geom_hline(yintercept = baselinectrl, linetype = "dashed", color = "red") +
  labs(title = "Earnings Inequality with control: 'Social Science' as baseline", x = "Fields of Study", y = "Earnings Differential ($)") +
  geom_text(aes(label = signif(Value)), nudge_y = 0.075, vjust = 1, color="black", size=3)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

Grouped by genders
```{r}
fs <- summary(F3)
ms <- summary(M3)


femalecof <- F3$coefficients[2:10]
femalese <- fs$coefficients[2:10,"Std. Error"]

malecof <- M3$coefficients[2:10]
malese <- ms$coefficients[2:10,"Std. Error"]

baselinefm <- 0

f <- data.frame(Category = names(femalecof), Value = femalecof, SE = femalese, Sex = "Female")
m <- data.frame(Category = names(malecof), Value = malecof, SE = malese, Sex = "Male")

fm <- rbind(f,m)

fm$Category <- factor(fm$Category, levels=c("Education", "Arts", "Other", "Biology","Health", "Physical", "Management","Engineering", "CompSci" ))
t_shift0 <- scales::trans_new("shift",
                             transform = function(x) {x-baselinefm},
                             inverse = function(x) {x+baselinefm})


dodge <- position_dodge(width=0.9)
limits <- aes(ymax=Value+SE,ymin=Value-SE)

ggplot(fm, aes(x=Category,y=Value,group=Sex, col=Category, fill=Category)) + 
  facet_wrap(~Sex) +
  geom_hline(yintercept=0, lwd=0.4, colour="grey50") +
  geom_errorbar(limits, position=dodge, width=0.25) +
  geom_point(position=dodge)+
  labs(title = "Earnings Inequality with control: 'Social Science' as baseline", x = "Fields of Study", y = "Earnings Differential ($)") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
